---
title: "Function Lab"
author: "Abbie M Popa"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part 1

(a) Write a function that takes a vector as input and returns the difference between the maximum value in a vector and the minimum value in a vector

```{r 1a}

```

(b) Make three vectors, on of the number 1 to 10, one of the even number 2 to 20, and one of the number 10 to 100 counting by 10s

```{r 1b}

```

(c) Run your function from part (a) on each of your vectors

```{r 1c}

```

(d) Make a vector of strings, `c("my", "name", "is", "bob")`, run your function from part (a) on this vector, what happens? (Note, remember to comment out lines of code that throw errors before knitting.)

```{r 1d}

```


(e) Make a matrix of the numbers 1 to 100 filled by row with 10 rows and 10 columns. 

```{r 1e}

```

(f) Use `apply` to run your function from (a) on all the rows of your matrix in part `e`, then run your function on all the columns.

```{r 1f}

```

## Part 2

(a) Write a function that takes a string, convers it to lower case, removes the words "a", "an" and "the", removes extra white spaces, then returns the new string. (Hint: use the `stringr` package.)

```{r 2a}
  library(stringr)

```

(b) Run your function on the `sentences` dataset (which comes with `stringr`). Print the first 10 new sentences.

```{r 2b}

```

(c) What happens if you run your function on a vector containing the numbers 1 through 10?

```{r 2c}

```
