---
title: "Lab in `ggplot2`"
output: pdf_document
---

```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = T)
```

Load ggplot2 into your current `R` session.

```{r libraries}
  library(ggplot2)
```

## Question 1

The `reshape2` package contains a dataset named `tips`, which contains information on dining trasactions. Load the `reshape2` package to gain access to this data (install it if you need to). Summary of the data follows:

```{r tips summary}
  library(reshape2)
  str(tips)
```

Create the following graphs:

(a) Plot `time` on x-axis, total_bill on the y-axis, colored by `smoker` and shaped by `sex`.


```{r 1a}
  
```

(b) `jitter` the previous plot so points are more visible

```{r 1b}
  
```

(c) Create the same plot with a "minimilist" theme

```{r 1c}
  
```

(d) Add a title to your plot

```{r 1d}
  
```

(e) Create a stacked bar graph with `time` on x-axis, `count` on the y-axis, filled by `sex`.

```{r 1e}
  
```

(f) Create a `dodge`d bar graph with `time` on x-axis, `count` on the y-axis, filled by `sex`.

```{r 1f}
  
```

(g) Change the color of your bars.

```{r 1g}
  
```


## Question 2

Create some fictional data using the following code:

```{r 2 setup}
  set.seed(22)
  x_int <- seq(10)
  x_fact <- factor(seq(10))
  y <- rnorm(10,2,13)
  myDF <- data.frame(x_int, x_fact, y)
```

Note the `type`s of each of the columns in `myDF`.

(a) Create a line graph with `x_int` on the x-axis and `y` on the y-axis.

```{r 2a}
  
```

(b) Add a title to you plot and make the title centered

```{r 2b}
  
```
(c) Add points to your plot

```{r 2c}
  
```

(d) Increase the font size

```{r 2d}
  
```
(e) Use the bw theme.

```{r 2e}
  
```

## Question 3

Create some fictional data using the following code:

```{r 3 set up, echo = T}
set.seed(33)
day <- rep(seq(7), 2)
stockPrice <- rnorm(14, 2, 13)
company <- c(rep("GOOG", 7), rep("APPL", 7))
myDF <- data.frame(day, stockPrice, company)
```

(a) Create a line and point graph with `day` on the x-axis and `stockPrice` on the y-axis, grouped by `company`.

```{r 3a}
  
```
(b) Make a boxplot of the stock data with one box for google's stock prices and one box for apple's stock prices. Make the color of the box different for each company.


```{r 3b}
  
```

## Question 4

(a) Using the dataframe "msleep" (which comes with ggplot2) make a histogram showing the sleep total values.

```{r 4a}
  
```

(b) Make the same histogram, this time with more bins (smaller binwidth)

```{r 4b}
  
```

(c) Make the same histogram, this time with fewer bins (larger binwidth)

```{r 4c}
  
```

(d) Read the documentation for "facet_wrap()". Use facet_wrap to make a plot with facets showing the "sleep_total" divided by "vore".

```{r 4d}
  
```