---
title: "Dplyr Join Lab"
author: "Abbie M Popa"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set-Up

You will need the following packages

```{r packages, message=FALSE}
  library(dplyr)
  library(ggplot2)
```

You will need the following data sets

```{r datasets}
  cust_ids <- read.csv("https://github.com/abbiepopa/BSDS100/raw/master/Data/cust_ids.csv")
  cust_rev <- read.csv("https://github.com/abbiepopa/BSDS100/raw/master/Data/cust_rev.csv")
  no_consent <- read.csv("https://github.com/abbiepopa/BSDS100/raw/master/Data/no_consent.csv")
```

The `cust_ids` data set contains a list of customers (`id_num`), whether they saw no ad, a picture ad, a text ad, or a video ad (`ad_type`) on a given visit to the site, and what location (`location`) they were viewing the website from.

The `cust_rev` data set contains a list of customers(`id_num`) and how much money they have spent, in total, through clicking on ads on the website.

The `no_consent` data set contains a list of customers who have asked to have their data removed from your training data under California's new consumer privacy law.

You want to determine what affect `ad_type` and `location` have on `money_spent`. You also must remove customers who have asked that their data be removed. Combine the data using functions we learned from `dplyr`. Then, visualise the effect of `ad_type` and `location` using plots.

```{r solution}

```

Based on your plot(s), what effect do you think `ad_type` and `location` have on `money_spent`?

