---
title: "Lecture3_Knitr_Exercise"
author: "Abbie M. Popa"
date: "8/20/2018"
output: pdf_document
---

# First make a new Rmd file

# Delete the example code, leaving the setup options

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load the guinea pig tooth growth data, look at the data, and read a description of it
```{r loading the data}
  data("ToothGrowth")
  ToothGrowth
  help("ToothGrowth")
```

# Display Column Names and Row Names for the Data
# Look at the 16th row of the data
# Look at the 3rd column of the data
# Look at the variable named "dose"
# Store a subset of the data, columns 1 and 3 and rows 24 - 48 for later use
# Store the supplement name for later use
```{r look at data}
  colnames(ToothGrowth)
  row.names(ToothGrowth)
  ToothGrowth[16, ]
  ToothGrowth[ , 3]
  ToothGrowth$dose
  tg_subset <- ToothGrowth[24:48, c(1,3)]
  tg_supp <- ToothGrowth$supp
```
# Challenge Question: In groups answer
## What are the different variables in the dataset?
`r variable.names(ToothGrowth)`

`r ?ToothGrowth`

## How many guinea pigs were used in the experiment?

## What are the different supplements used in the experiment?

`r summary(ToothGrowth)`

## What are the different doses used in the experiment?

# Calculate the 5-number summary for the dataset

```{r 5 num sum}
  summary(ToothGrowth)
```

# Challenge Question: What seems odd about the "dose" data? 

1st quartile equal min
3rd quartile equals max

# Make a table of supplement and dose information

```{r table explore}
  table(ToothGrowth$dose)
  table(ToothGrowth$supp, ToothGrowth$dose)
```


## Challenge Question: In groups create a visual representation of tooth growth based on dose and supplement condition

```{r plots}
  plot(ToothGrowth$dose, ToothGrowth$len)
  boxplot(ToothGrowth$dose, ToothGrowth$len)
  boxplot(ToothGrowth$len~ToothGrowth$supp*ToothGrowth$dose)
```


