---
title: "Wrangling Lab"
author: "Abbie M Popa"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set up

You will need the following packages for this lab

```{r load packages, message = F}
  library(dplyr)
  library(tidyr)
  library(magrittr)
  library(ggplot2)
```

## Baby Names

Install and load the `babynames` package using the following code:

```{r install baby names, eval = F}
  install.packages("babynames")
```

```{r load baby names}
  library(babynames)
```


**Please comment out the "install.packages" line of code before knitting!**

(1) Output a tibble indicating the number of births there were for each year in the dataset.

```{r q1}

```

(2) Output a tibble indicating the number of unique names there were for each year in the dataset.

```{r q2}

```

(3) Make (and save) a tibble with a column for each year/sex pair in the dataset and a column for the count of each pair

```{r q3}

```

(4) Use a `tidyr` function to separate your year,sex interaction column into a column for year and a column for sex. (hint1: make sure the interaction column is a character string!) (hint2: "." is a special character, like _, so will need to have two backslashes in front of it)

```{r q4}

```

(5) Make a bar plot showing the number of births each year where the color of the bar separates the counts by sex. "Dodge" your bars so they don't overlap. (hint: look up how we used stat = "identity" in class to make a bar plot)

```{r q5}

```


## Movies 

Install and load the `movies` data base using the following code 

```{r install movies, eval = F}
  install.packages("ggplot2movies")
```
```{r load movies}
  library(ggplot2movies)
```

**Be sure to comment out the "install.packages" line before knitting!**

(6) Look at the `movies` data frame using `str()`

```{r q6}

```

(7) Using a `dplyr` function, efficiently find all the columns named r# (e.g., r1, r2, r3, ...)

```{r q7}

```

(8) Using a `dplyr` function, find the means of all the r# columns

```{r q8}

```

(9) If you did the above without using pipes `%>%` from the `magrittr` package now do it with pipes. If you did it with pipes above, now do it without pipes

```{r q9}

```

(10) Using a `tidyr` function, efficiently gather all the r# columns into two long columns where the key is named "rater" and the value is named "rating". You can name the new data frame "long_movies"

```{r q10}

```

(11) Make a new even longer data frame "longer_movies" where the columns Action, Animation, Comedy, Drama, Documentary, Romance, and Short have the key "genre" and the value "encoding"

```{r q11}

```

(12) Remove all rows where encoding is equal to zero in longer_movies, leaving only rows where encoding equals 1. Also remove rows where the new rating column exceeds 15

```{r q12}

```

(13) If you did 12 the traditional way, now do it with filter, if you did 12 with filter, now do it the traditional way

```{r q13}

```

(14) Make a boxplot where each box represents a genre and the values are the ratings, please color your boxes by genre as well

```{r q14}

```

(15) Add a `facet_wrap` for rater

```{r q15}

```

(16) Which rater seems to like action movies more than they like other movies?



